### 2016-01-20 paper.tex
Fix typo
Reynold --> Reynolds

Analysis of the near-wake of the higher solidity UNH-RVAT turbine revealed that
vertical advection was the largest contributer to streamwise recovery
\cite{Bachant2015-JoT}, a trait which is considered an advantage of cross-flow
over axial-flow rotors in arrays \cite{Kinzel2012}. A similar analysis was
undertaken for the RM2, starting with the transport equation for mean kinetic
energy, rearranged to isolate the streamwise partial derivative (indices follow
the Einsteinian convention):
\begin{equation}
    \begin{split}
        \frac{\p K}{\p x}
        =
        \frac{1}{U}
        \bigg{[}
        & - \underbrace{V \frac{\p K}{\p y}}_{y\text{-adv.}}
        - \underbrace{W \frac{\p K}{\p z}}_{z\text{-adv.}}
        % Pressure work:
        - \frac{1}{\rho}\frac{\p}{\p x_j} P U_i \delta_{ij}
        % Work by viscous forces
        + \frac{\p}{\p x_j} 2 \nu U_i S_{ij}
        % Turbulent transport of K
        - \underbrace{
            \frac{1}{2}\frac{\p}{\p x_j} \overline{u_i' u_j'} U_i
        }_{\text{Turb. trans.}} \\
        % Production of k
        & + 
        \underbrace{
            \overline{u_i' u_j'} \frac{\p U_i}{\p x_j}
        }_{k\text{-prod.}}
        % Mean dissipation
        - 
        \underbrace{
            2 \nu S_{ij}S_{ij}
        }_{\text{Mean diss.}}
        \bigg{]}.
    \end{split}
    \label{eq:K-full}
\end{equation}

@@

Performance was assessed for Reynolds number dependence, showing a convergence
to a weakly $Re$-dependent linear regime at approximately $Re_D \approx 1 \times
10^6$ or $Re_{c,\mathrm{ave}} \approx 2 \times 10^5$. Comparison was made
between this turbine and the higher solidity UNH-RVAT, tested in nearly
identical conditions, which showed similar Reynold number thresholds but a
flatter linear regime, likely to due virtual camber of the higher
chord-to-radius ratio of the UNH-RVAT blades.

>>>>

Analysis of the near-wake of the higher solidity UNH-RVAT turbine revealed that
vertical advection was the largest contributor to streamwise recovery
\cite{Bachant2015-JoT}, a trait which is considered an advantage of cross-flow
over axial-flow rotors in arrays \cite{Kinzel2012}. A similar analysis was
undertaken for the RM2, starting with the transport equation for mean kinetic
energy, rearranged to isolate the streamwise partial derivative (indices follow
the Einsteinian convention):
\begin{equation}
    \begin{split}
        \frac{\p K}{\p x}
        =
        \frac{1}{U}
        \bigg{[}
        & - \underbrace{V \frac{\p K}{\p y}}_{y\text{-adv.}}
        - \underbrace{W \frac{\p K}{\p z}}_{z\text{-adv.}}
        % Pressure work:
        - \frac{1}{\rho}\frac{\p}{\p x_j} P U_i \delta_{ij}
        % Work by viscous forces
        + \frac{\p}{\p x_j} 2 \nu U_i S_{ij}
        % Turbulent transport of K
        - \underbrace{
            \frac{1}{2}\frac{\p}{\p x_j} \overline{u_i' u_j'} U_i
        }_{\text{Turb. trans.}} \\
        % Production of k
        & + 
        \underbrace{
            \overline{u_i' u_j'} \frac{\p U_i}{\p x_j}
        }_{k\text{-prod.}}
        % Mean dissipation
        - 
        \underbrace{
            2 \nu S_{ij}S_{ij}
        }_{\text{Mean diss.}}
        \bigg{]}.
    \end{split}
    \label{eq:K-full}
\end{equation}

@@

Performance was assessed for Reynolds number dependence, showing a convergence
to a weakly $Re$-dependent linear regime at approximately $Re_D \approx 1 \times
10^6$ or $Re_{c,\mathrm{ave}} \approx 2 \times 10^5$. Comparison was made
between this turbine and the higher solidity UNH-RVAT, tested in nearly
identical conditions, which showed similar Reynolds number thresholds but a
flatter linear regime, likely to due virtual camber of the higher
chord-to-radius ratio of the UNH-RVAT blades.
